resistanceModelNotesAndy

### 2016-03-01 paper1_results_figs.Rmd
findreplace mix2_minus with mixA_minus

  #df_diff$mix2_minus_seq0.25 <- df_diff["gen_cP0.25"] - df_diff["gen_cP0.25seq"]
  df_diff["mix2_minus_seq0.25"] <- df_diff["gen_cP0.25"] - df_diff["gen_cP0.25seq"]

  #TODO : later do PRCC on df_diff["mix2_minus_seq0.25"]

@@

    y <- "mix2_minus_seq0.25"

@@

    x <- df_diff[,1:num_inputs]
    y <- df_diff["mix2_minus_seq0.25"]

@@

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             ggtitle(paste("PRCC difference between sequential and mixture2")) +
             xlab(NULL)
          )

@@

## Andys questions 
1. In mixtures what causes resistance to the 2nd insecticide to arise more slowly when the first insecticide is removed from the mixture ?

>>>>

  #df_diff$mixA_minus_seq0.25 <- df_diff["gen_cP0.25"] - df_diff["gen_cP0.25seq"]
  df_diff["mixA_minus_seq0.25"] <- df_diff["gen_cP0.25"] - df_diff["gen_cP0.25seq"]

  #TODO : later do PRCC on df_diff["mixA_minus_seq0.25"]

@@

    y <- "mixA_minus_seq0.25"

@@

    x <- df_diff[,1:num_inputs]
    y <- df_diff["mixA_minus_seq0.25"]

@@

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             ggtitle(paste("PRCC difference between sequential and mixture adaptive")) +
             xlab(NULL)
          )

@@
